### 2024-05-19 fantasy-football.qmd
20240519 - edits

The goal in football is for a team to score more points than their opponent.

@@

The team with the ball (i.e., the offense) has four opportunities ("downs") to advance the ball 10 yards.
A team can advance the ball either by running it or passing and catching it.
At the end of a rushing play, the ball advances to wherever the ball carrier is tackled or goes out of bounds (i.e., wherever the player is "down").
At the end of a passing play, if the thrown ball is caught (i.e., a completed pass), the ball advances to wherever the ball carrier is tackled or goes out of bounds.
If the thrown ball is not caught (i.e., an incomplete pass), the ball does not advance.
Wherever the ball is advanced to dictates where the next play begins.
The yard position on the field where the next play takes place from is known as the "line of scrimmage".
Neither team can cross the line the line of scrimmage until the next play begins.
To begin the play, the ball is placed on the line of scrimmage and the Center gives (or "snaps") the ball to the Quarterback.

@@

A field goal involves a kicker kicking the ball with an intent to kick the ball through the field goal posts ("uprights").
To achieve points, the field goal must be above the cross bar and be in between the uprights (extended vertically) when it crosses the cross bar.

>>>>

### The Objective {#sec-football}

The goal in football is for a team to score more points than their opponent.
A game lasts 60 minutes, and it is separated into four 15-minute quarters.
The team with the most points when the time runs out wins.

@@

The team with the ball (i.e., the offense) has four opportunities ("downs") to advance the ball 10 yards.
A team can advance the ball either by running it or passing and catching it.
At the end of a rushing play, the ball advances to wherever the ball carrier is tackled or goes out of bounds (i.e., wherever the player is "down").
At the end of a passing play, if the thrown ball is caught (i.e., a completed pass), the ball advances to wherever the ball carrier is tackled or goes out of bounds.
If the thrown ball is not caught in bounds before the ball hits the ground (i.e., an incomplete pass), the ball does not advance.
Wherever the ball is advanced to dictates where the next play begins.
The yard position on the field where the next play takes place from is known as the "line of scrimmage".
Neither team can cross the line the line of scrimmage until the next play begins.
To begin the play, the ball is placed on the line of scrimmage and the Center gives (or "snaps") the ball to the Quarterback.

@@

A field goal involves a kicker kicking the ball with an intent to kick the ball through the field goal posts ("uprights").
To score points by making a field goal, the kicked ball must go between the uprights (extended vertically) and over the cross bar.
